%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer, Product} % Job title
    {Lifesum} % Organization
    {Stockholm, Sweden} % Location
    {Oct. 2018-} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Standardized microservices using Python, Docker and AWS, and implemented ways to generate microservices using automation.}
      \item {Data ETL pipelines and backend microservices created and shipped to millions of customers worldwide using Python and SQL.}
      \item {Responsible for machine learning efforts company wide, working with teams to integrate machine learning in the mobile application.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Eningeer, Product} % Job title
    {Tictail (Shopify)} % Organization
    {Stockholm, Sweden} % Location
    {Aug. 2017 - Sept. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for all machine learning efforts company wide, worked closely with all teams in Stockholm \& New York.}
        \item {Research, development and deployment of machine learning models and its infrastructure, for internal use \& in production.}
        \item {Full stack responsibilities, backend and data engineering, focused on problems within personalization, recommendation, ranking, search, natural language processing and customer analytics using Python \& SQL.}
        \item {Created data and machine learning infrastructure from scratch using Python, SQL, Dcoker, AWS and AirFlow in order to conduct machine learning engineering throughout the company.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Research Intern, Search \& Voice} % Job title
    {Spotify} % Organization
    {Stockholm, Sweden} % Location
    {Jan. 2017 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research and implementation of machine learning models for search, recommendation \& ranking.}
        \item {Data engineering pipelines \& optimizations, processing billions of rows of data using SQL, Scala, Java \& GCP.}
        \item {Worked with the team to ship the final model into production, known as the Play Me Something feature on the Spotify Voice client.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern, Siri} % Job title
    {Apple} % Organization
    {Cupertino, California} % Location
    {Jun. 2016 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data centered approaches for analyzing and improving Siri interactions for iOS for all domains.}
        \item {Developed iOS \& watchOS tools with C/C++/Objective-C/Swift for extracting and analyzing Siri intent, domain \& language data, used by thousands of Apple employees.}
        \item {Worked with Siri Media/QA teams on improving data automation pipelines.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern, Product} % Job title
    {EF Education First} % Organization
    {London, U.K.} % Location
    {Jun. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed several features in production, worked with QA and backend teams for solving critical bugs in the iOS client using Objective-C/Swift.}
      \item {Researched data and machine learning centered approaches for future backend services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile Applications Engineer} % Job title
    {Microsoft} % Organization
    {Stockholm, Sweden} % Location
    {Aug. 2013 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and researched mobile applications for the Windows and Windows Phone 8/8.1 platform for app generation \& automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
